---
title: "assignment_5 - Starter Rmd"
author: "metts"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# If you need/want to make a page break in PDF output, you can use the following code snippet:

\newpage

# This is the section following the `\newpage` page break for PDF.

Remember, typically first load your needed libraries. This week the processing was done in the assignment script; thus we can actually skip loading libraries.

Second, make sure to position your median income plot followed by your owner-occupied plot. Notice that `echo=FALSE` is set as a parameter to hide the code chunk printing in the final document which gives a cleaner look:

```{r, fig.width=10, fig.height=7, echo=FALSE}
# Load the saved ggplot object
map_equal_MI_plot <- readRDS("~/Desktop/assignment_5/results/map_equal_MI.rds")

# Display the loaded plot
print(map_equal_MI_plot)
```



```{r, fig.width=10, fig.height=7, echo=FALSE}
# Load the saved ggplot object
map_equal_OO_plot <- readRDS("~/Desktop/assignment_5/results/map_equal_OO.rds")

# Display the loaded plot
print(map_equal_OO_plot)
```

```{r echo=FALSE, fig.width=25, fig.height=15, fig.align="left", out.width="100%"}
```


## Findings Section:

Your findings writeup should be placed here.












