---
title: "assignment_3 - Starter Rmd"
author: "metts"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## This is a Title/Header
### This is a Title/Header but smaller
#### This is a Title/Header but smaller

This is body text.

When you click the **Knit** button at the top a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. 

You can embed R code chunks as follows. First we load the arrest data, then plot a variable via the barplot approach.

```{r}
#load the arrest data into the .Rmd document before proceeding to any plot development
load("~/Desktop/assignment_2/results/arrestNYC.RData")
```

```{r}
arrest_counts_boro <- table(arrestNYC$ARREST_BORO)
barplot(arrest_counts_boro,
        main = "Arrest in NYC by Arrest Borough (Jan-June 2025)",
        xlab = "Borough",
        ylab = "Count",
)
```

Note that at the top for knitr options, echo is set to TRUE; this will result in the code chunks being printed as well as the executed output.  For your assignment, you can choose which you prefer: if set to FALSE, only the code chunk executed action will result without the code itself printing into the document.


Review the cheatsheet for `.Rmd` for all the things that you can do with this type of R output.  Here are some examples that you might want to include in your assignment 2 deliverable:

- [This is a link.](link url)
- > block quotes
- horizontal rule:

---











