---
title: "assignment_3 - Starter Rmd"
author: "metts"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## This is a Title/Header
### This is a Title/Header but smaller
#### This is a Title/Header but smaller

This is body text.

When you click the **Knit** button at the top a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. 

Remember to first load your needed libraries.

```{r}
#load needed libraries.
library(tidycensus)
library(tidyverse)
library(ggthemes)
```

Second, we load the LES race data, then plot the LES census tract profile.

```{r}
#load the Lower East Side race data that was cleaned/saved from the assignment_3 script.
load("~/Desktop/lab_3/results/LES_race_data_evaluated.RData")
```


```{r race_composition_plot, echo=FALSE, fig.width=15, fig.height=8, fig.align="center", out.width="100%"}
#note the figure dimensions set prior to plotting in .Rmd
ggplot(LES_race_data_evaluated, aes(x = NAME, y = Percentage, fill = Race_Category)) +
  geom_bar(stat = "identity", position = "fill") +
  labs(
    title = "Racial Composition of Lower East Side Neighborhood (NTA) Census Tracts",
    x = "Census Tract",
    y = "Percentage",
    fill = "Race Category",
    caption = "Source: 2020 US Decennial Census, PL 94-171"
  ) +
  scale_y_continuous(labels = scales::percent) +
  theme_fivethirtyeight() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    axis.title.y = element_text(face = "bold"),
    legend.position = "right",
    axis.text.x  = element_text(angle = 45, hjust = 1, vjust = 1)
  )
```

Third, we load the saved comparison NTA race data, replacing the example here for LES:

```{r}
#load the comparison race data that was cleaned/saved from the assignment_3 script; adapt the code chunk from current LES data.
load("~/Desktop/lab_3/results/LES_race_data_evaluated.RData")
```

Fourth, we load the comparison NTA race data, then plot the comparison census tract profile.  To follow is the code chunk for LES repeated; make sure to revise the code chunk accordingly for your comparison NTA.

```{r race_composition_plot_comparison, echo=FALSE, fig.width=15, fig.height=8, fig.align="center", out.width="100%"}
#note the figure dimensions set prior to plotting in .Rmd
ggplot(LES_race_data_evaluated, aes(x = NAME, y = Percentage, fill = Race_Category)) +
  geom_bar(stat = "identity", position = "fill") +
  labs(
    title = "Racial Composition of Comparison (NTA) Census Tracts",
    x = "Census Tract",
    y = "Percentage",
    fill = "Race Category",
    caption = "Source: 2020 US Decennial Census, PL 94-171"
  ) +
  scale_y_continuous(labels = scales::percent) +
  theme_fivethirtyeight() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    axis.title.y = element_text(face = "bold"),
    legend.position = "right",
    axis.text.x  = element_text(angle = 45, hjust = 1, vjust = 1)
  )
```

Note that at the top for knitr options, echo is set to TRUE; this will result in the code chunks being printed as well as the executed output.  For your assignment, you can choose which you prefer: if set to FALSE, only the code chunk executed action will result without the code itself printing into the document.

Review the cheatsheet for `.Rmd` for all the things that you can do with this type of R output.  Here are some examples that you might want to include in your assignment 2 deliverable:

- [This is a link.](link url)
- > block quotes
- horizontal rule:

---











