---
title: "assignment_4 - Starter Rmd"
author: "metts"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## This is a Title/Header
### This is a Title/Header but smaller
#### This is a Title/Header but smaller

This is body text.

When you click the **Knit** button at the top a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. 

Remember to first load your needed libraries.

```{r}
#load needed libraries.
library(tidycensus)
library(tidyverse)
library(gt)
```

Second, make sure to load the either option 1 Poverty Rate table or option 2 Rent Burden table.  In both cases the file is named `compare_tbl` and it is saved in the `results` folder:

```{r}
#load the option 1 or option2 data frame that was cleaned/saved from the assignment_4 script.
load("~/Desktop/assignment_4/results/compare_tbl.RData")
```

```{r}
#load the settings for the comparison plot and chart
#for option 1, paste here lines #14 - #36 from the Poverty Rate script.
#for option 2, paste here lines #13 - 50 from the Rent Burden script.



```


```{r echo=FALSE, fig.width=12, fig.height=8, fig.align="center", out.width="100%"}
#revise the code listing for the comparison plot
#for option 1, paste here lines #142 - #168 from the Poverty Rate script.
#for option 2, paste here lines #210 - #233 from the Rent Burden script.

```


```{r echo=FALSE, fig.width=25, fig.height=15, fig.align="left", out.width="100%"}

#revise the code listing for the comparison chart
#for option 1, paste here lines #170 - #205 from the Poverty Rate script.
#for option 2, paste here lines #235 - #272 from the Rent Burden script

```


## Findings Section:

Your findings writeup should be placed here.












