---
title: "assignment_6 - Starter Rmd"
author: "metts"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# If you need/want to make a page break in PDF output, you can use the following code snippet:

\newpage

# This is the section following the `\newpage` page break for PDF.

Remember, typically first load your needed libraries. This week the processing was done in the assignment script; thus we only need to load the `gt` library in order to render the frequency table correctly:

```{r, echo=FALSE}
library(gt)
```

Second, make sure to position your frequency table followed by your land use PUMA plot. Notice that `echo=FALSE` is set as a parameter to hide the code chunk printing in the final document which gives a cleaner look.


## Frequency Table for Land Uses in Chosen PUMA:

```{r, fig.width=10, fig.height=7, echo=FALSE}
# Load the frequency table
freq_tbl <- readRDS("~/Desktop/assignment_6/results/freq_tbl.rds")

#make necessary changes to the labeling in gt table for chosen PUMA
freq_tbl |>
   gt(rowname_col = "LandUse_code") |>
   tab_header(title = md("**PUMA 4103 — Parcels by Land Use (PLUTO)**")) |>
   cols_label(
     label = "Category",
     n = "Count",
    percent = "Percent"
   )

```

## Land Use Plot:

```{r, fig.width=10, fig.height=7, echo=FALSE}
# Load the saved ggplot object
landuse_plot <- readRDS("~/Desktop/assignment_6/results/landuse_plot.rds")

# Display the loaded plot
print(landuse_plot)
```

## Findings Section:

Your findings writeup should be placed here.












